---
title       : The Sample Mean Compared to The Real Mean
subtitle    : The Shiny App
author      : Roman Kierzkowski
job         : Data Scientis
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The Application

The Shiny app I prepared compares the real mean with the sample mean.
It draws samples from normal distribution which parameters can be adjusted.

--- .class #id 

## Variance Influence

When you increase the variance the difference usually increases.
```{r, echo=FALSE}
    x <- rnorm(10, mean = 0, sd = 5)
    hist(x, breaks = 50, col = 'darkgray', border = 'white', xlim=c(-10,10))
    sample_mean = mean(x)
    legend("topright", c('real mean', 'sample mean'), col=c(2,3), lwd=2)
    abline(v=0, col=2, lwd=3)
    abline(v=sample_mean, col=3, lwd=3)
```

--- .class #id 

## Sample Size Influence

When you increase the sample size the discrepancy between the means decreases.
```{r, echo=FALSE}
    x <- rnorm(100, mean = 0, sd = 5)
    hist(x, breaks = 50, col = 'darkgray', border = 'white', xlim=c(-10,10))
    sample_mean = mean(x)
    legend("topright", c('real mean', 'sample mean'), col=c(2,3), lwd=2)
    abline(v=0, col=2, lwd=3)
    abline(v=sample_mean, col=3, lwd=3)
```

--- .class #id 

## Thank you!

* Thank you for checking my project!
* Hope you enjoy it!
* Please, be forgiving.

--- .class #id 









